Optimal Symmetric Multimodal Templates and Concatenated Random Forests for Supervised Brain Tumor Segmentation (Simplified) with \textit{ANTsR}

### 2014-04-01 paper.tex
WIP: mild comments

\subsubsection{Miscellaneous Multimodal Feature Image Generation}
\label{sec:misc}

In addition to the feature images outlined in the previous sections, 
several other feature images were generated largely based on what 
had been used in previous work.  For each modality, several images
were generated based on calculation of voxelwise neighborhood 
first-order statistics including mean, variance, skewness, and entropy
using neighborhood block radii
of 1 and 3 voxels.  We also calculated two Euclidean distance
transforms \citep{maurer2003} to be used for each subject.  One was
calculated from the subject's own cerebral mask and the other was the 
distance transform of the symmetric template cerebral mask warped
to the subject.  Finally, we also generated the  (T1 - T1C) difference 
image \citep{prastawa2003}.
The script {\tt createFeatureImages.sh} performs all preprocessing
and generates all feature images.  In Figure \ref{fig:featureImages} we provide sample mid-axial 
image slices from features generated from the {\tt BRATS\_HG0301} data set.

>>>>

\subsubsection{Miscellaneous Multimodal Feature Image Generation}
\label{sec:misc}
Our strategy for feature selection was to, first, generate an ample feature
set and to, second, use the training phase to prioritize the features
appropriately.  In principal, this will eliminate weak features and
retain strong ones even in the presence of substantial noise (cite
some RF paper here ...).
In addition to the feature images outlined in the previous sections, 
several other feature images were generated largely based on what 
had been used in previous work.  For each modality, several images
were generated based on calculation of voxelwise neighborhood 
first-order statistics including mean, variance, skewness, and entropy
using neighborhood block radii
of 1 and 3 voxels.  We also calculated two Euclidean distance
transforms \citep{maurer2003} to be used for each subject.  One was
calculated from the subject's own cerebral mask and the other was the 
distance transform of the symmetric template cerebral mask warped
to the subject.  Finally, we also generated the  (T1 - T1C) difference 
image \citep{prastawa2003}.
The script {\tt createFeatureImages.sh} performs all preprocessing
and generates all feature images.  In Figure \ref{fig:featureImages} we provide sample mid-axial 
image slices from features generated from the {\tt BRATS\_HG0301} data set.
